Analysis of pudding following Davidson 1970

### 2021-11-05 inst/pudding.Rmd
more work

Now use it:

@@

so according to `samep.test()` the puddings are all the same strength.

@@

@@

```{r,synthmaker}
set.seed(0)
f <- function(i){rmultinom(1,50,prob=h[i,])} # f(i) = sample from row i of h
synth <- pudding_table
synth[,-(1:3)] <- t(sapply(1:15,f))  # random sample
synth[,3] <- 50
rownames(synth) <- rownames(p)
colnames(synth) <- colnames(p)
synth
```

>>>>

@@

so according to `samep.test()` the puddings are all the same strength.
We note that the propensity to tie cannot possibly be zero but we can
give a profile likelihood curve:

```{r,calcptie,cache=TRUE}
ptie <- seq(from=0.08,len=20,to=0.15)
l <- profsupp(pudding,"tie",ptie)
```

```{r}
plot(ptie,l,type='b',lwd=2)
abline(h=c(0,-2))
#abline(v=c(0.095,0.127))
grid()
```

and we see that a credible interval for the proclivity to tie would be
$(0.095,0.127)$.

@@

We can see above that the first-mover advantage is small (and indeed a
"second-mover advantage") is also very small.

@@

```{r,synthmaker}
set.seed(0)
f <- function(i){rmultinom(1,50,prob=h[i,])} # f(i) = sample from row i of h
synth <- pudding_table
synth[,-(1:3)] <- t(sapply(1:15,f))  # random sample
synth[,3] <- 50
rownames(synth) <- rownames(p)
colnames(synth) <- colnames(p)
showsome(synth)
```
